%====================
% EXPERIENCE A
%====================
\subsection{\texorpdfstring{Full-stack Developer / Airline Ticket Booking Website \hfill Sep 2025 --- Present}{ROLE / PROJECT A - MMM YYYY --- Present}}
\begin{zitemize}
    \item Developed a full-stack booking system feature and management feature for an airline ticket booking website.
    \item Technologies: Java, Spring Boot, MySQL, React, Git, Nginx.
    \item Github Repository: \href{https://github.com/tongthanhdat009/Airline-Ticket-Booking-Website}{github.com/tongthanhdat009/Airline-Ticket-Booking-Website}
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{\texorpdfstring{Full-stack Developer / School Bus Scheduling Web \hfill Sep 2025 --- Dec 2025}{ROLE / PROJECT D - MMM YYYY --- MMM YYYY}}
\begin{zitemize}
    \item Built a full-stack app to manage school bus schedules (MVP), handle real-time route data and an admin dashboard.
    \item Technologies: ReactJS, Node.js, ExpressJS, MySQL, Overleaf, Git.
    \item Repository Front-end: \href{https://github.com/tongthanhdat009/cnpm-frontend}{github.com/tongthanhdat009/School Bus Scheduling App - Front-end}
    \item Github Repository Back-end: \href{https://github.com/tongthanhdat009/cnpm-backend}{github.com/tongthanhdat009/School Bus Scheduling App - Back-end}
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\subsection{\texorpdfstring{Full-stack Developer / Store Mangagement Web \hfill Sep 2025 --- Dec 2025}{ROLE / PROJECT E - MMM YYYY --- MMM YYYY}}
\begin{zitemize}
   \item Developed a full-stack store management web app with features for a grocery store. Implemented a Blazor-based admin dashboard for data visualization and reporting.
   \item Technologies: Vue.js, Node.js, .Net, Blazor, Git, C\#.
   \item Repository Admin Dashboard: \href{https://github.com/tongthanhdat009/dotnet-frontend}{github.com/tongthanhdat009/store-management-admin-dashboard}
   \item Repository Client: \href{https://github.com/tongthanhdat009/BlazorApp}{github.com/tongthanhdat009/client-blazor-app}
   \item Repository Back-end: \href{https://github.com/tongthanhdat009/dotnet-backend}{github.com/tongthanhdat009/store-management-backend}
\end{zitemize}

% ====================
% QA Tester / Quality Assurance for E-commerce Web App
% ====================
\subsection{\texorpdfstring{QA Tester / Quality Assurance for E-commerce Web App \hfill Sep 2024 --- Mar 2025}{ROLE / PROJECT B - MMM YYYY --- MMM YYYY}}
\begin{zitemize}
    \item Ensured the quality and functionality of an e-commerce web app. My role involved both Manual Testing and Automation Testing using Selenium, as well as API testing with Postman.
    \item Testing Report: \href{https://docs.google.com/document/d/1a2b3c4d5e6f7g8h9i0j1k2l3m4n5o6p7q8r9s0t1u2v3w4x5y6z7/edit?usp=sharing}{View Testing Report} 
    \item Technologies: Manual \& Automation Testing, Postman, Selenium, Java, PHP.
\end{zitemize}

%====================
% Mobile Developer / Android Instagram Clone
%====================
% \subsection{\texorpdfstring{Mobile Developer / Android Instagram Clone \hfill Sep 2024 --- Dec 2024}{ROLE / PROJECT C - MMM YYYY --- MMM YYYY}}
% \begin{zitemize}
%     \item Developed an Android Instagram clone with core features (posts, live feed). 
%     \item Built the UI and integrated Firebase for all real-time back-end services.
%     \item Technologies: Java, Android Studio, Firebase, Git.
%     \item Github Repository: \href{https://github.com/tongthanhdat009/Instargram-Clone}{github.com/tongthanhdat009/Instargram-Clone}
% \end{zitemize}



%====================
% EXPERIENCE F
%====================
%\subsection{\texorpdfstring{ROLE / PROJECT F \hfill MMM YYYY --- MMM YYYY}{ROLE / PROJECT F - MMM YYYY --- MMM YYYY}}
%\subtext{company F \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE G
%====================
%\subsection{\texorpdfstring{ROLE / PROJECT G \hfill MMM YYYY --- MMM YYYY}{ROLE / PROJECT G - MMM YYYY --- MMM YYYY}}
%\subtext{company G \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE H
%====================
%\subsection{\texorpdfstring{ROLE / PROJECT H \hfill MMM YYYY --- MMM YYYY}{ROLE / PROJECT H - MMM YYYY --- MMM YYYY}}
%\subtext{company H \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE I
%====================
%\subsection{\texorpdfstring{ROLE / PROJECT I \hfill MMM YYYY --- MMM YYYY}{ROLE / PROJECT I - MMM YYYY --- MMM YYYY}}
%\subtext{company I \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}